\documentclass{homework}
\course{Math 6701}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration} The final theorem of our triad, Stokes' theorem,
first appeared in print in 1854.  George Stokes had for several years
been setting the Smith's Prize Exam at Cambridge, and in the February,
1854, examination, question \#8 is the following\ldots \byline{Victor
  Katz, in \textit{The History of Stokes' Theorem}}
% Math magazine, Vol. 52, No. 3 (May, 1979), pp. 146-156.
\end{inspiration}

\section{Terminology}

\begin{problem}
  For a smooth manifold $M$, define $H^k_{\dR}(M)$.
\end{problem}

\section{Numericals}

\begin{problem}
Consider the form $\omega \in \Omega^k(\R^n)$ given by
\[
  \omega = \sum_{i=1}^n (-1)^{i-1} x_i \, dx_1 \wedge \cdots \wedge \widehat{dx_i} \wedge \cdots \wedge dx_n.
\] Let $S^{n-1} \subset \R^n$ be the unit sphere with $i : S^{n-1} \to
\R^n$ the inclusion.

Compute $d\omega$.

Then compute $\int_{S^{n-1}} \omega$, perhaps using ``well-known''
facts about volume.
\end{problem}

\begin{problem}
 Is $\omega$ closed?  Is $\omega$ exact?  Is $i^\star \omega$ closed?  Exact?
\end{problem}

\section{Exploration}

\begin{problem} Show that the wedge product of forms descends to a
product on cohomology.
\end{problem}

\begin{problem} The $n$-disk $D^n$ has the $(n-1)$-sphere as its
boundary; write $i : S^{n-1} \to D^n$ for the inclusion map.  We say
that $r : S^{n-1} \to D^n$ is a \textbf{retraction} if $r \circ i =
\id_{\partial D^n}$.

Can you find a retraction of the disk onto its boundary?
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem}
 A smooth map $f : D^n \to D^n$ has a fixed point. 
\end{problem}


\begin{problem}
  Suppose the smooth manifold $M$ is decomposed as the union of two open sets $M = U \cup V$ with $U \cap V \neq \varnothing$.  Then there is a short exact sequence of de Rham complexes
  \[
    0 \longrightarrow \Omega^\star(U \cup V) \longrightarrow \Omega^\star(U) \oplus \Omega^\star(V) \longrightarrow \Omega^\star(U \cap V) \longrightarrow 0.
 \]
\end{problem}

\begin{problem}
  The de Rham cohomology of the $n$-sphere $S^n$ is
  \[
    H_{\dR}^k(S^n) = \begin{cases}
      \R & \mbox{if $k = 0$,} \\
      0 & \mbox{if $k \neq 0, \, k \neq n$, and }\\
      \R & \mbox{if $k = n$.}
      \end{cases}
  \]
\end{problem}

\begin{problem}
  Let $X \in \Gamma(TS^n)$ be a vector field.  For all $p \in S^n$, the vector $X_p$ is nonzero. 
\end{problem}

\end{document}
