\documentclass{homework}
\course{Math 6701}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
  Vietoris lived to be 110 years and 309 days old, and became the oldest verified Austrian man ever.
  \byline{The Wikipedia article on Leopold Vietoris}
\end{inspiration}

With the Fall Break, this shorter problem set is now \textbf{extra
credit}.

\section{Terminology}

\begin{problem}\label{symplectic-definition}What is a \textbf{symplectic} manifold?
\end{problem}

\begin{problem}
 For a map $f : S^{2n-1} \to S^n$, define the \textbf{Hopf invariant} $H(f)$.
\end{problem}

\section{Numericals}

\begin{problem}
For the Hopf map $f : S^3 \to S^2$ from \ref{hopf-map}, compute the Hopf invariant $H(f)$.
\end{problem}

\section{Exploration}

\begin{problem}
  In defining mapping degree last week, we used a \textbf{volume form}.

  If $\omega \in H_{\dR}^2(M)$ is a symplectic form, show that $\omega^n$ is a volume form.
  \end{problem}

  \begin{problem}
  Does $S^2 \times S^2$ admit a symplectic form?
\end{problem}

\begin{problem} The word ``complex'' is Latin, while ``symplectic'' is
built from the same words, but in Greek (a process the linguists call
a \textit{calque}).  The underlying meaning is a ``tying together'' so
what does a symplectic form tie together?  A symplectic form $\omega$
``ties together'' the tangent and cotangent spaces.  Given a form $dH
\in \Omega^1(M)$, the symplectic form can be used to produce a vector
field $V_H \in \Gamma(TM)$.

So why do we assume that $\omega$ is closed?  Use \ref{cartan-formula}
to show that if $\omega$ is closed, then $\omega$ is constant along
flow lines of $V_H$.
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem} For odd $n$ and smooth maps $f : S^{2n-1} \to S^n$,
the Hopf invariant $H(f)$ vanishes.
\end{problem}


\end{document}
