\documentclass{homework}
\course{Math 6701}
\author{Jim Fowler}
\input{preamble}

\begin{document}
\maketitle

\begin{inspiration}
  Having thus refreshed ourselves in the oasis of a proof, we now turn
  again into the desert of definitions. \byline{T.~Br\"ocker and
    K.~J\"anich in \textit{Introduction to differential topology}}
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is a \textbf{chart}?  What is an \textbf{atlas}?
\end{problem}

\begin{problem}
  What is a \textbf{smooth map} between smooth manifolds?

  What is a \textbf{diffeomorphism} between smooth manifolds?
\end{problem}

\section{Numericals}

\begin{problem}
  Describe a smooth atlas for $\RP^n$.
\end{problem}

\begin{problem}
  Describe a smooth atlas for $\Gr(k,\C^n)$, the \textbf{Grassmannian}
  parameterizing the $k$-dimensional subspaces of the $n$-dimensional
  space $\C^n$.

  How many charts did you use?
\end{problem}

\section{Exploration}

\begin{problem}
  Is every continuous bijection $f : \R \to \R$ a homeomorphism?

  Is every smooth bijection $f : \R \to \R$ a diffeomorphism?  
\end{problem}

\begin{problem}
  Suppose $M^n$ is a topological $n$-manifold and $N^n$ is a smooth
  $n$-manifold.  Further suppose there is a homeomorphism
  $f : M \to N$.

  Explain how to use $f$ to pullback the smooth structure on $N$ to
  produce a smooth structure on $M$.  Is the resulting smooth manifold
  diffeomorphic to $N$?
\end{problem}

\begin{problem}
  For positive integers $n$ and $m$, describe infinitely many distinct
  nonconstant smooth maps $\CP^n \to \CP^m$.
\end{problem}


\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\textit{You may not have met these PODASIP-style problems before.
  What follows are statements which may be ``true'' or ``false.''  If
  the statement is true, you must provide a proof.  If the statement
  is false, explain why it is false, then fix the statement and
  finally supply a proof for the repaired statement.}

\begin{problem}
  The uncountable disjoint union of copies of $\mathbb{R}$ is a manifold.
\end{problem}

\begin{problem}
  Every connected smooth 1-manifold is diffeomorphic to the circle $S^1$.
  
  \textit{Hint:} Salvage this false statement, and summarize the
  appendix of Milnor's \textit{Topology from the differentiable
    viewpoint} in your own words.
\end{problem}

\begin{problem}
  The smooth manifolds $\RP^1$ and $S^1$ are diffeomorphic.
\end{problem}

\end{document}
