\documentclass{homework}
\course{Math 6701}
\author{Jim Fowler}
\input{preamble}

\DeclareMathOperator{\GL}{GL}

\begin{document}
\maketitle

\begin{inspiration}
  Why is differential geometry the study of a connection on a principal bundle?
  \byline{R.~W.~Sharpe in \textit{Differential Geometry: Cartan's Generalization of Klein's Erlangen Program}}
\end{inspiration}

\section{Terminology}

\begin{problem}
 What is a fiber bundle? 
\end{problem}

\begin{problem}
  What is a principal $G$-bundle?
\end{problem}

\begin{problem}
  What is a principal $G$-connection on a principal $G$-bundle? 
\end{problem}

\section{Numericals}

\begin{problem} Suppose $G \subset \GL(V)$ and consider the principal
$G$-bundle $G \to \{\star\}$, i.e., the principal $G$-bundle of $G$
over the one point space $\star$.
  
Describe a principal $G$-connection on this bundle as a $\mathfrak{g}$-valued 1-form.

\textit{Hint:}
 Consider the \textit{Mauer-Cartan form}.
\end{problem}

\section{Exploration}

\begin{problem} Given a vector bundle $E \to M$, we can build $F(E)
\to M$, the frame bundle associated to $E$.

  Given a principal $\GL(\R^n)$-bundle on $M$, we can form an
$n$-dimensional ``associated'' vector bundle on $M$.

Are these procedures (of constructing the frame bundle and of
constructing the associated vector bundle) inverse to each other?  Why
or why not?
\end{problem}

\begin{problem}
  Recall the Hopf map $f : S^3 \to S^2$.  Is this a principal $S^1$-bundle?
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem}
 Every principal $\Z/2\Z$-bundle is also a principal $S^1$-bundle. 
\end{problem}

\begin{problem} % oriented is a missing hypothesis
 Every circle bundle is also a principal $S^1$-bundle. 
\end{problem}

\begin{problem}
  If a vector bundle admits a global section, then it is trivial.
\end{problem}


\end{document}
