\documentclass{homework}
\course{Math 6701}
\author{Jim Fowler}
\input{preamble}

\DeclareMathOperator{\GL}{GL}

\begin{document}
\maketitle

\begin{inspiration}
  Meta-theorem 2.2.3: Any canonical construction in linear algebra gives rise to a geometric version for holomorphic vector bundles. \byline{Daniel Huybrechts in \textit{Complex Geometry: An Introduction}}
\end{inspiration}

\section{Terminology}

\begin{problem}
  What is a vector bundle?  What is a \textit{complex} vector bundle?
\end{problem}

\begin{problem}
 For a vector bundle $E \to Y$ over a smooth manifold $Y$, and a smooth map $f : X \to Y$, define the pullback $f^\star E$.
\end{problem}

\begin{problem}
  What is the tautological line bundle over $\RP^n$?
\end{problem}

\section{Numericals}

\begin{problem} Suppose $E \to M$ is an $n$-dimensional real vector
bundle over a smooth manifold $M$, with an open cover $\{U_i\}$
trivializing the bundle.  The transition functions are maps $g_{ij} :
U_i \cap U_j \to \GL_n(\R)$.

  Compute the transition functions for the dual bundle $E^\star \to M$.
\end{problem}

\section{Exploration}

\begin{problem}
  Is $TS^1$ trivial?  What about $TS^3$?  What about $TG$ for a Lie group $G$?
\end{problem}

\begin{problem}
 Is $TS^2$ trivial?   Why or why not?
\end{problem}

\begin{problem} If $TM$ is not trivial but $E \to M$ is trivial, can
  it happen that $TM \oplus E$ is trivial?

  We say that $TM$ is
\textbf{stably trivial} in this case.
\end{problem}

\begin{problem} Is the tautological line bundle over $\RP^1$
isomorphic to $T\RP^1$?
\end{problem}

\begin{problem}
  Classify line bundles over $S^1$ up to isomorphism.
\end{problem}

\section{Prove or Disprove and Salvage if Possible (PODASIP)}

\begin{problem}
For a closed manifold $M$ and a vector bundle $E \to M$, there is a bundle $F \to M$ so that $E \oplus F$ is trivial.
\end{problem}

\end{document}
