\documentclass{homework}
\input{preamble}
\author{Jim Fowler}
\course{Math 6701}
\date{Week 12: Geometry}

\begin{document}
\maketitle

Last week, we learned about vector bundles, which lets us do linear
algebra over a manifold.  This week is about ``geometry'' and by
geometry, I mean calculus---being able to take derivatives of sections
of a vector bundle.  We do this with a gadget called a
\textbf{connection}.  The name \textit{connection} is suggestive: the
fibers above distant points are ``connected'' via parallel transport.

It is not immediately clear that being able to take derivatives of
sections of vector bundles really amounts to doing geometry; once we
have connections, we can discuss \textbf{curvature} which is
undoubtably something geometric.  Perhaps our first experience with
curvature has to do with \textbf{holonomy} as we perform parallel
transport around closed curves.  To learn about this, read Morita's
\textit{Geometry of Differential Forms} focusing on
\begin{itemize}
\item 5.3 Connections in vector bundles
\end{itemize}

It's always important to make connections to our prior learning.  A
couple weeks ago, we first met \textit{forms}, and this week, we'll
find, after choosing a connection, we can produce a certain closed
differential form --- that is, a cohomology class -- and that class is
independent of the choice of connection.  This is our first
\textbf{characteristic class}.  Read
\begin{itemize}
\item 5.4 Pontrjagin classes
\end{itemize} to learn about these.  Characteristic classes will be a
big theme next week!

\end{document}
