\documentclass{homework}
\input{preamble}
\author{Jim Fowler}
\course{Math 6701}
\date{Week 10: Harmonic forms}

\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{5}

\begin{document}
\maketitle

This marks a departure from what we've been studying!  With some
cohomological methods in our toolkit, we now consider \textit{harmonic
forms}. What are these?

But first, what's the problem that harmonic forms are trying to solve?
A cohomology class is first of all just that---a equivalence class.
We saw when showing that the Hopf invariant is well-defined the
bookkeeping required to handle the fact that the \textit{same} class
might be represented by different forms.  If only there were a
canonical repersentative in each class!

In the presence of a Riemannian metric, we can trade covectors for
vectors.  The resulting relationship between 1-forms and vector fields
permits us to solve the aforementioned problem: we can choose a
canonical representative by choosing a form which is
\textit{harmonic}, in the sense that the Laplacian $\Delta$ of the
form is zero.

To dig into this, open Morita's \textit{Geometry of Differential Forms} and read
\begin{itemize}
\item 4.1 Differential forms on Riemannian manifolds
\item 4.2 Laplacian and harmonic forms
\item 4.3 The Hodge theorem
\end{itemize} As applications, we'll again discuss Poincar\'e duality
and the K\"unneth formula and Euler characteristic, and finally meet
the \textbf{signature}, an interesting invariant.




\end{document}
